Off the beaten path: \\ Gaia reveals GD-1 stars outside of the main stream

### 2018-05-01 paper/gd1.tex
rephrase fig4 caption

\begin{figure}
\begin{center}
\includegraphics[width=\textwidth]{features.pdf}
\end{center}
\caption{
Color-magnitude and proper-motion diagrams of fields associated with a spur above GD-1 (top), and fields related to the blob below GD-1 (bottom).
The top and bottom left panels show properties in stream fields (darkest rectangles in middle panel), both middle panels present spur and blob (medium rectangles), while the right-most top and bottom panels are selected opposite from spur and blob (lightest rectangles).
Selection boxes are shown in all CMD and proper-motion panels as shaded regions.
Both the spur and the blob fields have more stars in the CMD selection box than the corresponding control fields.
Proper motions of these stars follow the distribution of stars in adjacent stream fields, thus confirming the association of these off-track features with GD-1.
}
\label{fig:features}
\end{figure}

>>>>

\begin{figure}
\begin{center}
\includegraphics[width=\textwidth]{features.pdf}
\end{center}
\caption{
Color-magnitude and proper-motion diagrams of fields associated with a spur above GD-1 (top), and fields related to the blob below GD-1 (bottom).
Panels on the left show properties in stream fields (darkest rectangles in middle panel), middle panels present spur and blob (medium rectangles), and the right-most panels are control fields on the opposite sides from spur and blob (lightest rectangles).
% The top and bottom left panels show properties in stream fields (darkest rectangles in middle panel), middle panels present spur and blob (medium rectangles), while the right-most top and bottom panels are selected opposite from spur and blob (lightest rectangles).
Selection boxes are shown in all CMD and proper-motion panels as shaded regions.
Both the spur and the blob fields have more stars in the CMD selection box than the corresponding control fields.
Proper motions of these stars follow the distribution of stars in adjacent stream fields, thus confirming the association of these off-track features with GD-1.
}
\label{fig:features}
\end{figure}
